Quantifying Stability and Change in Personal Culture Using Panel Data

### 2023-09-23 manuscript.Rmd
improve prominance of edu case in the intro

This pattern of results helps clarify and, hopefully, transcend previous debates. What is more, the measure we propose offers a quantity with more diverse applications than a simple judgment about whether change happened. To exemplify this, we apply the measure to explore differences in the relative importance of intrapersonal change for people with and without college degrees, comparing both within and across questions in ways that the tournament of models cannot. The results suggest new directions for further clarifying the theoretical mechanisms that shape personal cultural change over the life course.

>>>>

These results help clarify and, hopefully, transcend previous debates. What is more, the measure we propose offers a tool with wider utility than merely discerning durable change that can help advance theoretical debates. To exemplify this, we turn to the role of education for cultural differences. Specifically, we use our measure to better understand what mechanisms might underlie differences observed between people with and those without college degrees. Focusing on eight questions that tab general political dispositions, our measure enables us to compare the relative importance of intrapersonal change for both groups in ways that the tournament of models cannot. We find less evidence of durable change among those with college degree. This may imply that the college experience predominantly serves as a formative period that solidifies political dispositions, rather than fostering an openness [ADAPTABILITY?] to new information and influences later in the life. [MISSING AN ENDING SENTENCE NOW.]
